\input{preamble}												% Preamble 
\raggedbottom													% LaTeX don't "strech" the text

%\includeonly{file1,file2}										% Inkluder only specific files

\begin{document}												% Start document
\frontmatter													% nummbers with roman numbers
\include{Chapters/Frontpage/_Frontpage}
%\include{Chapters/_Resume}
\begin{abstract}
	\thispagestyle{empty}
	Reinforcement learning is nowadays improving rapidly with the new ideas from deep learning. This thesis gives a clear explanation of the theory in reinforcement learning. The state-of-the-art methods in deep reinforcement learning are explained, implemented and tested. We present the A3C method which can make an agent learn how to control a car in a car simulation environment. It is a lightweight framework because it can be trained on a single multi-core CPU instead of a GPU. The input used in our A3C method is only the raw image from the car simulator, and the output is a set of actions for controlling the car. The implemented A3C method is optimized by trying different test scenarios. The trained agent can drive without being interrupted by obstacles in the environment.     
\end{abstract}
\newpage
\mbox{}
\thispagestyle{empty}
\newpage
%%%% content (TOC) %%%%
\tableofcontents*												%content (called ToC) 


\mainmatter														% main part - numbered frompage 1
\include{Chapters/Introduction/Introduction}
\include{Chapters/TheoreticalBackground/TheoreticalBackground}
\include{Chapters/Architecture/Architecture}
\include{Chapters/Results/Results}
\include{Chapters/Discussion/Discussion}
\include{Chapters/Conclusion/Conclusion}

%\include{Kapitler/Referencer}



%%%% References %%%%
\begingroup
\raggedright
\bibliography{References/References}							
% Litteraturlisten inkluderes
\endgroup

%%%% Fixme-list %%%%
\newpage														% New page to Fixme-list
%\listoffixmes													% Fixme-list - removes in the end with "%"

%%%% Appendix %%%%
\appendix														% Appendix start - gives chapters letters instead of numbers
\clearforchapter												% Secure that the pagestyle activates on the right page
\phantomsection													% artificial chapter that hyperlinks can  'maintain in'
\pdfbookmark[0]{Appendiks}{appendiks}							% gives the possibility to clickable bookmark for the final PDF

\end{document}													% finnish document - required